---
title: "LTPP Summary Report"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the rutting, rougness and texture data from the LTPP database.  

The code to generate this is displayed first - then the graphics.  
  
Use the menu to left to go straight to the Rutting, Roughness and Texture plots.  
  

# Data Importing
The code below imports the rutting, roughness and texture data from the 10m databases  
  
```{r import data, fig.height=10, fig.width=12, echo=TRUE}

#Sys.Date()
Sys.time()

#load database connection library
library(RODBC)
 
#connect to database 
db <- "C:/local_databases/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2021.mdb"

con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

```

## Importing tables

```{r import table data, fig.height=10, fig.width=12, echo=TRUE}

Rutting10m <- sqlFetch(con2, "10mRutting")
Texture10m <- sqlFetch(con2, "10mTexture")
Roughness10m <- sqlFetch(con2, "10mRoughness")
Rating50m <- sqlFetch(con2, "50mRating")
CalibrationSections <- sqlFetch(con2, "CalibrationSections")

```

#Data tidy

```{r Data tidy Info data, fig.height=10, fig.width=12, echo=TRUE}

# Create SH/LA column
library(dplyr)
library(stringr)

CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA")) %>% arrange(OwnerType, CAL_SECTION_ID)

Rutting10m <- Rutting10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
Texture10m <- Texture10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
Roughness10m <- Roughness10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
Rating50m<- Rating50m%>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))

```

# LTPP Sites

```{r CalibrationSections, fig.height=10, fig.width=12, echo=TRUE}

CalibrationSections <- CalibrationSections %>%select(-COMMENTS)

library(kableExtra)
kable(CalibrationSections, format = "html", caption = "LTPP Sites") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")


```

# Rutting

```{r plot Rutting10m , fig.height=40, fig.width=12, echo=TRUE}

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10m, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10m, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

# Roughness Plots


```{r plot Roughness10m , fig.height=40, fig.width=12, echo=TRUE}

# View(Roughness10m)

library(dplyr)
Roughness10mL <- Roughness10m %>% filter(LwpIRI < 25)
Roughness10mR <- Roughness10m %>% filter(RwpIRI < 25)
Roughness10mLN <- Roughness10m %>% filter(LaneIRI < 25)

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mL, aes(x=FinancialYear, y=LwpIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("LWP Roughness (IRI)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

ggobj2 <- ggplot(data=Roughness10mR, aes(x=FinancialYear, y=RwpIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("RWP Roughness (IRI)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

ggobj2 <- ggplot(data=Roughness10mLN, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("Lane Roughness (IRI)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

#Texture Plots

```{r plot Texture10m , fig.height=20, fig.width=12, echo=TRUE}

#View(Texture10m)

library(dplyr)
Texture10mL <- Texture10m %>% filter(LWPTxt < 10)
Texture10mR <- Texture10m %>% filter(RWPTxt < 10)


library(ggplot2)
ggobj2 <- ggplot(data=Texture10mL, aes(x=FinancialYear, y=LWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Texture10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("LWP Texture MPD (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

ggobj2 <- ggplot(data=Texture10mR, aes(x=FinancialYear, y=RWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Texture10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + ylab("RWP Texture MPD (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

close(con2)
```

