---
title: "LTPP Ratings Report"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the Visual Ratings from the LTPP database.  

The code to generate this is displayed first - then the graphics.  
  
Use the menu to left to go straight to the Rating type for all sites.    
  
# Data Importing
The code below imports the data from the Ratings in the database

```{r import data, fig.height=10, fig.width=12, echo=TRUE}

#Sys.Date()
Sys.time()

#setup plot theme for plots
#library(ggplot2)
#mytheme <- theme_grey() + theme(text = element_text(colour = "black", size=18))


#load database connection library
library(RODBC)
 
#connect to database 1 - CAPTIF PR3 0404.mdb
db <- "C:/DDATA/LTPP/2020/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2020.mdb"

#con2 <- odbcConnectAccess2007(db)
con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

```

## Importing tables

```{r import table data, fig.height=10, fig.width=12, echo=TRUE}

#Check column names of a table 
#sqlColumns(con2, "Profilometer Profiles")$COLUMN_NAME


Rating50m <- sqlFetch(con2, "50mRating")
CalibrationSections <- sqlFetch(con2, "CalibrationSections")


```

#Data tidy

```{r Data tidy Info data, fig.height=10, fig.width=12, echo=TRUE}

# Create SH/LA column
library(dplyr)
library(stringr)


CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA"))

View(CalibrationSections)
#print(CalibrationSections)

Rating50m<- Rating50m%>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))

```

# All Rating 50m - plots!

```{r plot Rating 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}

#View(Rutting10m)

library(ggplot2)
```

## ALoss%

```{r plot ALoss 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`ALoss%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m ALoss% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## SLoss%

```{r plot SLoss 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}


ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`SLoss%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m SLoss% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## ChipLoss%

```{r plot ChipLoss 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`ChipLoss%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m ChipLoss% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Delam%

```{r plot Delam 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Delam%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Delam% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## MechDamage%

```{r plot MechDamage 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`MechDamage%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m MechDamage% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Flush-Low%

```{r plot Flush-Low 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Flush-Low%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Flush-Low% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Flush-Mid%

```{r plot Flush-Mid 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Flush-Mid%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Flush-Mid% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Flush-High%

```{r plot Flush-High 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Flush-High%`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Flush-High% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongE-N%

```{r plot LongE-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongE-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongE-N% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongE-W%

```{r plot LongE-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongE-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongE-W% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongE-S%

```{r plot LongE-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongE-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongE-S% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongWT-N%

```{r plot LongWT-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongWT-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongWT-N% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongWT-W%

```{r plot  LongWT-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongWT-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongWT-W% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongWT-S%

```{r plot LongWT-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongWT-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongWT-S% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongIR-N%

```{r plot LongIR-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongIR-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongIR-N% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongIR-W%

```{r plot LongIR-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongIR-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongIR-W% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## LongIR-S%

```{r plot LongIR-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`LongIR-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m LongIR-S% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Trans-N%

```{r plot Trans-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Trans-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Trans-N% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Trans-W%

```{r plot Trans-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Trans-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Trans-W% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Trans-S%

```{r plot Trans-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Trans-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m Trans-S% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlG-N

```{r plot AlG-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlG-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlG-N Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlG-W

```{r plot AlG-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlG-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlG-W Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlG-S

```{r plot AlG-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlG-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlG-S Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlWT-N

```{r plot AlWT-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlWT-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlWT-N Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlWT-W

```{r plot AlWT-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlWT-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlWT-W Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## AlWT-S

```{r plot AlWT-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`AlWT-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m AlWT-S Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PAR-N

```{r plot PAR-N 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PAR-N`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PAR-N Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PAR-W

```{r plot PAR-W 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PAR-W`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PAR-W Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PAR-S

```{r plot PAR-S 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PAR-S`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PAR-S Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PatchSurf

```{r plot PatchSurf 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PatchSurf`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PatchSurf Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PatchStructure 

```{r plot PatchStructure  50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PatchStructure`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PatchStructure Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PotholeDiameter

```{r plot PotholeDiameter 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PotholeDiameter`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PotholeDiameter Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PotholeDepth

```{r plot PotholeDepth 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PotholeDepth`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PotholeDepth Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## PotholeNumber

```{r plot PotholeNumber 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`PotholeNumber`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m PotholeNumber Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## EdgeA

```{r plot EdgeA 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`EdgeA`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m EdgeA Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## EdgeD

```{r plot EdgeD 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`EdgeD`, col = as.factor(LANE_DIRECTION))) +  geom_boxplot() + ggtitle("Rating50m EdgeD Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)
```

## Shoving%

```{r plot Shoving 50m , fig.height=40, fig.width=12, echo=TRUE, eval = TRUE}
ggobj2 <- ggplot(data=Rating50m, aes(x=FinancialYear, y=`Shoving%`, col = as.factor(LANE_DIRECTION))) + geom_boxplot() + ggtitle("Rating50m Shoving% Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
print(ggobj2)

close(con2)

```
