---
title: "LTPP Roughness Detail Report"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the roughness from the LTPP database.  

The code to generate this is displayed first - then the graphics.  
  
Use the menu to left to go straight to the roughness for all sites, State Highway sites, Local Authority sites or Individual sites.  

# Data Importing
The code below imports the data from the 10m databases

```{r import data, fig.height=40, fig.width=12, echo=TRUE}

#Sys.Date()
Sys.time()

#load database connection library
library(RODBC)

db <- "C:/DDATA/LTPP/2019/LTPP 2018-19 database/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2019.mdb"

con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

Roughness10m <- sqlFetch(con2, "10mRoughness")
CalibrationSections <- sqlFetch(con2, "CalibrationSections")

library(tidyverse)
Councils <- CalibrationSections %>% filter(is.na(Region)) %>% group_by(NMA) %>% summarise()

# Create SH/LA column
library(dplyr)
library(stringr)

CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA"))

Roughness10m <- Roughness10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
```

# All Roughness Plots

```{r plot Roughness10m on A3, fig.height=40, fig.width=12, echo=TRUE}

# View(Roughness10m)

library(dplyr)
Roughness10mL <- Roughness10m %>% filter(LwpIRI < 25)
Roughness10mR <- Roughness10m %>% filter(RwpIRI < 25)
Roughness10mLN <- Roughness10m %>% filter(LaneIRI < 25)

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mL, aes(x=FinancialYear, y=LwpIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("LWP Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)

ggobj2 <- ggplot(data=Roughness10mR, aes(x=FinancialYear, y=RwpIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("RWP Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)

ggobj2 <- ggplot(data=Roughness10mLN, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)
```

# SH Site Roughness

```{r plot Roughness10m SH Site on A3, fig.height=40, fig.width=12, echo=TRUE}

#SH Sites

Roughness10mLNSH <- Roughness10mLN %>% filter(OwnerType == "SH")

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mLNSH, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)
```

# SH CAL Sites

```{r plot Roughness SH CAL Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#SH CAL Sites

Roughness10mLNSHCAL <- Roughness10mLNSH %>% filter(stringr::str_detect(SECTION_ID, "CAL"))

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mLNSHCAL, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CAL Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)
```

# SH CS Sites

```{r plot Roughness SH Cs Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#SH Cs Sites

Roughness10mLNSHCS <- Roughness10mLNSH %>% filter(stringr::str_detect(SECTION_ID, "CS"))

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mLNSHCS, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CS Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)
```

# LA Site Roughness

```{r plot Roughness10m LA Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#LA Sites

Roughness10mLNSH <- Roughness10mLN %>% filter(OwnerType == "LA")

library(ggplot2)
ggobj2 <- ggplot(data=Roughness10mLNSH, aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("LA Roughness10m Lane Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 
print(ggobj2)
```

# Big individual Roughness plots 

```{r plot  Big individual  Roughness plots , fig.height=12, fig.width=20, echo=TRUE}

library(dplyr)
ggobj2Roughness10m <- Roughness10m %>% group_by(SECTION_ID) %>% do(plots=ggplot(data=.) +
         aes(x=FinancialYear, y=LaneIRI, col = as.factor(LANE_DIRECTION)) +  geom_boxplot() + labs(col = "I/D") + ggtitle("Roughness - Lane IRI", subtitle = .$SECTION_ID)) + ylab("Lane Roughness (IRI)") + xlab("Financial Year") 

print(ggobj2Roughness10m$plots)
```

