---
title: "LTPP Rutting Detail Report"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the rutting  from the LTPP database.  

The code to generate this is displayed first - then the graphics.  
  
Use the menu to left to go straight to the Rutting for all sites, State Highway sites, Local Authority sites or Individual sites.  

# Data Importing
The code below imports the data from the 10m databases

```{r import data, fig.height=40, fig.width=12, echo=TRUE}

Sys.time()

#load database connection library
library(RODBC)
 
db <- "C:/DDATA/LTPP/2020/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2020.mdb"

con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

Rutting10m <- sqlFetch(con2, "10mRutting")

CalibrationSections <- sqlFetch(con2, "CalibrationSections")

# Create SH/LA column
library(dplyr)
library(stringr)

CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA"))

Rutting10m <- Rutting10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
```


# All Sites Rutting

```{r plot Rutting10m on A3, fig.height=40, fig.width=12, echo=TRUE}

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10m, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10m, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)
```

# SH Site Rutting

```{r plot Rutting10m SH Site on A3, fig.height=40, fig.width=12, echo=TRUE}

#SH Sites

Rutting10mSH <- Rutting10m %>% filter(OwnerType == "SH")

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10mSH, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10mSH, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5)  + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)
```

# SH CAL Sites

```{r plot Rutting10m SH CAL Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#SH CAL Sites

Rutting10mSHCAL <- Rutting10mSH %>% filter(stringr::str_detect(SECTION_ID, "CAL"))

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10mSHCAL, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CAL Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10mSHCAL, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CAL Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5)  + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

```

# SH CS Sites

```{r plot Rutting10m SH CS Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#SH CS Sites

Rutting10mSHCS <- Rutting10mSH %>% filter(stringr::str_detect(SECTION_ID, "CS"))

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10mSHCS, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CS Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10mSHCS, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH CS Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5)  + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

```

# LA Site Rutting

```{r plot Rutting10m LA Site on A3, fig.height=20, fig.width=12, echo=TRUE}

#LA Sites

Rutting10mLA <- Rutting10m %>% filter(OwnerType == "LA")

library(ggplot2)
ggobj2 <- ggplot(data=Rutting10mLA, aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("LA Rutting10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5) + ylab("LWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

ggobj2 <- ggplot(data=Rutting10mLA, aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("LA Rutting10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol =5)  + ylab("RWP Rutting (mm)") + xlab("Financial Year") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D")
print(ggobj2)

```

# Big individual rutting plots LWP

```{r plot Rutting10m Big individual rutting plots LWP on A3, fig.height=12, fig.width=20, echo=TRUE}

library(dplyr)
ggobj2LWPrut <- Rutting10m %>% group_by(SECTION_ID) %>% do(plots=ggplot(data=.) +
         aes(x=FinancialYear, y=LWP, col = as.factor(LANE_DIRECTION)) +  geom_boxplot() + labs(col = "I/D") + ggtitle("LWP Rut", subtitle = .$SECTION_ID) + ylab("LWP Rutting (mm)") + xlab("Financial Year"))  

print(ggobj2LWPrut$plots)
```

# Big individual rutting plots RWP

```{r plot Rutting10m Big individual rutting plots RWP on A3, fig.height=12, fig.width=20, echo=TRUE}

ggobj2RWPrut <- Rutting10m %>% group_by(SECTION_ID) %>% do(plots=ggplot(data=.) +
         aes(x=FinancialYear, y=RWP, col = as.factor(LANE_DIRECTION)) +  geom_boxplot() + labs(col = "I/D") + ggtitle("RWP Rut", subtitle = .$SECTION_ID) + ylab("RWP Rutting (mm)") + xlab("Financial Year")) 

print(ggobj2RWPrut$plots)
close(con2)
```
