---
title: "LTPP Data Tables"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the data tables in the LTPP database that don't track distress but identify a property of the sites.  

The code to generate this is displayed first - then the table.  
  
Use the menu to left to go straight to the table required.    

The FWD data table only displays the first few lines as it is very large.   

# Data Importing
The code below imports the data that are tables in the databases - a bit ugly thanks to large field names

```{r import data, fig.height=10, fig.width=12, echo=TRUE}

#Sys.Date()
Sys.time()

#load database connection library
library(RODBC)
 
#connect to database 1 - CAPTIF PR3 0404.mdb
db <- "C:/DDATA/LTPP/2019/LTPP 2018-19 database/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2019.mdb"

#con2 <- odbcConnectAccess2007(db)
con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

# find all tables
library(knitr)
LTPPtables <-(sqlTables(con2, tableType = "TABLE")$TABLE_NAME)
kable(LTPPtables, format = "html", caption = "Tables in LTPP Database")
```

## Importing tables

```{r import table data, fig.height=10, fig.width=12, echo=TRUE}

#Check column names of a table 
#sqlColumns(con2, "Profilometer Profiles")$COLUMN_NAME


CalibrationSections <- sqlFetch(con2, "CalibrationSections")
CAL_SEC_PAVE_DATA <- sqlFetch(con2, "CAL_SEC_PAVE_DATA")
CAL_SEC_PAVE_WIDTH <- sqlFetch(con2, "CAL_SEC_PAVE_WIDTH")
CAL_SEC_RAINFALL_DATA <- sqlFetch(con2, "CAL_SEC_RAINFALL_DATA")
CAL_SEC_SNP_DATA <- sqlFetch(con2, "CAL_SEC_SNP_DATA")
CAL_SEC_SURF_DATA <- sqlFetch(con2, "CAL_SEC_SURF_DATA")
CAL_SEC_TRAFFIC_DATA <- sqlFetch(con2, "CAL_SEC_TRAFFIC_DATA")
NIWA2017 <- sqlFetch(con2, "NIWA weather monthly rainfall as at July 2017")
NIWAlink <- sqlFetch(con2, "NIWA weather sites & calibration sections link")
FWDHeader <- sqlFetch(con2, "OTHER-FallingWeightDeflectometerHeader")
FWDData <- sqlFetch(con2, "OTHER-FallingWeightDeflectometer")
AdditionalInfoPaveLayer <- sqlFetch(con2, "tAdditionalInfoPaveLayer")
TestPitSummary <- sqlFetch(con2, "Test Pit Summary")
AdditionalInfoPenetrationTest <- sqlFetch(con2, "tAdditionalInfoPenetrationTest")

```

# Data Tables 
The code below displays data tables

## LTPP Sites

```{r CalibrationSections, fig.height=10, fig.width=12, echo=TRUE}

# Create SH/LA column
library(dplyr)
library(stringr)


CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA")) %>% arrange(OwnerType, CAL_SECTION_ID)

View(CalibrationSections)

CalibrationSections <- CalibrationSections %>%select(-COMMENTS)

library(kableExtra)
kable(CalibrationSections, format = "html", caption = "LTPP Sites") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## CAL_SEC_PAVE_DATA

```{r CAL_SEC_PAVE_DATA, fig.height=10, fig.width=12, echo=TRUE}

kable(CAL_SEC_PAVE_DATA, format = "html", caption = "CAL_SEC_PAVE_DATA") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## CAL_SEC_PAVE_WIDTH

```{r width data, fig.height=10, fig.width=12, echo=TRUE}


kable(CAL_SEC_PAVE_WIDTH, format = "html", caption = "CAL_SEC_PAVE_WIDTH") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

##CAL_SEC_RAINFALL_DATA

```{r rain data, fig.height=10, fig.width=12, echo=TRUE}

kable(CAL_SEC_RAINFALL_DATA, format = "html", caption = "CAL_SEC_RAINFALL_DATA") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## SNP Data
```{r SNP data, fig.height=10, fig.width=12, echo=TRUE}

kable(CAL_SEC_SNP_DATA, format = "html", caption = "CAL_SEC_SNP_DATA") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```
## CAL_SEC_SURF_DATA
```{r iCAL_SEC_SURF_DATA data, fig.height=10, fig.width=12, echo=TRUE}
kable(CAL_SEC_SURF_DATA, format = "html", caption = "CAL_SEC_SURF_DATA") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## CAL_SEC_TRAFFIC_DATA
```{r CAL_SEC_TRAFFIC_DATA data, fig.height=10, fig.width=12, echo=TRUE}

kable(CAL_SEC_TRAFFIC_DATA, format = "html", caption = "CAL_SEC_TRAFFIC_DATA") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## NIWA2017 Rain
```{r NIWA2017, fig.height=10, fig.width=12, echo=TRUE}
kable(NIWA2017, format = "html", caption = "NIWA2017 Rain") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## NIWAlink
```{r NIWAlink data, fig.height=10, fig.width=12, echo=TRUE}
kable(NIWAlink, format = "html", caption = "NIWA link data") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## FWD Headers

```{r FWDHeader data, fig.height=10, fig.width=12, echo=TRUE}

kable(FWDHeader, format = "html", caption = "FWDHeader") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## Head of FWD Data

```{r FWDData data, fig.height=10, fig.width=12, echo=TRUE}
kable(head(FWDData), format = "html", caption = "FWD Data") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

##Summary of layer Info
```{r layer Info data, fig.height=10, fig.width=12, echo=TRUE}
#View(AdditionalInfoPaveLayer)
kable(AdditionalInfoPaveLayer, format = "html", caption = "Additional Info on Pavement Layers") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```


## Summary of a testpits
```{r testpits Info data, fig.height=10, fig.width=12, echo=TRUE}
#View(TestPitSummary)
kable(TestPitSummary, format = "html", caption = "Test Pit Summary") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```

## Summary of Scalas
```{r Scalas Info data, fig.height=10, fig.width=12, echo=TRUE}
#View(AdditionalInfoPenetrationTest)
kable(AdditionalInfoPenetrationTest, format = "html", caption = "Scalas") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```


## Summary of AdditionalInfoPenetrationTestDetail
```{r ltestpits Info data, fig.height=10, fig.width=12, echo=TRUE}
AdditionalInfoPenetrationTestDetail <- sqlFetch(con2, "tAdditionalInfoPenetrationTestDetail")
#View(AdditionalInfoPenetrationTestDetail)
kable(AdditionalInfoPenetrationTestDetail, format = "html", caption = "AdditionalInfoPenetrationTestDetail") %>%
  kable_styling("striped", fixed_thead = T) %>% scroll_box(width = "100%", height = "500px")
```


##Photo listing - not operational
```{r photos data, fig.height=10, fig.width=12, echo=TRUE}
#TmpImportTmp <- sqlFetch(con2, "TmpImportTmp") #Photo listing
#View(TmpImportTmp)
```

#Councils with LTPP sites

```{r councils data, fig.height=10, fig.width=12, echo=TRUE}

library(tidyverse)
Councils <- CalibrationSections %>% filter(is.na(Region)) %>% group_by(NMA) %>% summarise()
kable(Councils, format = "html", caption = "Councils with LTPP Sites") %>%
  kable_styling("striped", fixed_thead = T) 
```

