---
title: "LTPP Texture Detail Report"
output:
  html_document:
    toc: true
    toc_float: true
---
This page contains a national summary of the texture from the LTPP database.  

The code to generate this is displayed first - then the graphics.  
  
Use the menu to left to go straight to the texture for all sites, State Highway sites, Local Authority sites or Individual sites.  
  
# Data Importing
The code below imports the data from the 10m databases

```{r import data, fig.height=10, fig.width=12, echo=TRUE}

#Sys.Date()
Sys.time()

#load database connection library
library(RODBC)
 
db <- "C:/DDATA/LTPP/2019/LTPP 2018-19 database/NZTA_SH&LA_LTPPData_IntCalib_1Jul2001-30Jun2019.mdb"

con2 <- odbcDriverConnect(paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)}; DBQ=", db))

Texture10m <- sqlFetch(con2, "10mTexture")
CalibrationSections <- sqlFetch(con2, "CalibrationSections")

library(tidyverse)
Councils <- CalibrationSections %>% filter(is.na(Region)) %>% group_by(NMA) %>% summarise()

# Create SH/LA column
library(dplyr)
library(stringr)

CalibrationSections <- CalibrationSections %>% mutate(OwnerType = if_else((str_detect(CAL_SECTION_ID, "CAL")|str_detect(CAL_SECTION_ID, "CS")), "SH", "LA"))

Texture10m <- Texture10m %>% left_join(CalibrationSections, by = c("SECTION_ID"="CAL_SECTION_ID"))
```

#Texture Plots

## All texture plots

```{r plot Texture10m on A3, fig.height=20, fig.width=12, echo=TRUE}

library(dplyr)
Texture10mL <- Texture10m %>% filter(LWPTxt < 10)
Texture10mR <- Texture10m %>% filter(RWPTxt < 10)

library(ggplot2)
ggobj2 <- ggplot(data=Texture10mL, aes(x=FinancialYear, y=LWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Texture10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("LWP Texture MPD (mm)") + xlab("Financial Year") 
print(ggobj2)

ggobj2 <- ggplot(data=Texture10mR, aes(x=FinancialYear, y=RWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("All Texture10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("RWP Texture MPD (mm)") + xlab("Financial Year") 
print(ggobj2)

```

## SH texture plots

```{r plot SH Texture10m on A3, fig.height=20, fig.width=12, echo=TRUE}

#SH Sites

Texture10mLSH <- Texture10mL  %>% filter(OwnerType == "SH")
Texture10mRSH <- Texture10mR  %>% filter(OwnerType == "SH")


library(ggplot2)
ggobj2 <- ggplot(data=Texture10mLSH, aes(x=FinancialYear, y=LWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH Texture10m LWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("LWP Texture MPD (mm)") + xlab("Financial Year") 
print(ggobj2)

ggobj2 <- ggplot(data=Texture10mRSH, aes(x=FinancialYear, y=RWPTxt, col = as.factor(LANE_DIRECTION))) +
  geom_boxplot() + ggtitle("SH Texture10m RWP Boxplot") + facet_wrap(~SECTION_ID, ncol=5) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + labs(col = "I/D") + ylab("RWP Texture MPD (mm)") + xlab("Financial Year") 
print(ggobj2)


```

## LA texture plots - none exist

```{r plot LA Texture10m on A3, fig.height=28, fig.width=40, eval = FALSE}

#LA Sites

Texture10mLLA <- Texture10mL  %>% filter(OwnerType == "LA")
Texture10mRLA <- Texture10mR  %>% filter(OwnerType == "LA")

```

## Big individual texture plots LWP

```{r plot Big individual texture plots LWP, fig.height=12, fig.width=20, echo=TRUE}

library(dplyr)
ggobj2Texture10mL <- Texture10mL %>% group_by(SECTION_ID) %>% do(plots=ggplot(data=.) +
         aes(x=FinancialYear, y=LWPTxt, col = as.factor(LANE_DIRECTION)) +  geom_boxplot() + labs(col = "I/D") + ggtitle("LWP Texture", subtitle = .$SECTION_ID) + ylab("LWP Texture MPD (mm)") + xlab("Financial Year"))   

print(ggobj2Texture10mL$plots)
```

## Big individual texture plots RWP

```{r plot Big individual texture plots RWP, fig.height=12, fig.width=20, echo=TRUE}

library(dplyr)
ggobj2Texture10mR <- Texture10mR %>% group_by(SECTION_ID) %>% do(plots=ggplot(data=.) +
         aes(x=FinancialYear, y=RWPTxt, col = as.factor(LANE_DIRECTION)) +  geom_boxplot() + labs(col = "I/D") + ggtitle("RWP Texture", subtitle = .$SECTION_ID) + ylab("RWP Texture MPD (mm)") + xlab("Financial Year"))   

print(ggobj2Texture10mR$plots)
close(con2)
```
